\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-05-16 Papers/ViscousInstabilities/article_figure1.tex
working-updated

>>>>

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_vel_magn.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) single inlet velocity magnitude   
}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_vel_magn.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) double inlet velocity magnitude   
}
}     
\caption{For the same time step, t=1000, these plots describe the velocity magnitudes of the phase $1$ (injected fluid) under the same boundary and initiall conditions. From top to bottom,these graphs describe the velocity magnitude %for fixed mesh is plotted(top), the velocity magnitude 
for adaptive mesh-single inlet (top) and the velocity magnitude for adaptive mesh with double inlet (bottom) as these are also presented in fig.\ref{fig:3testcase_a}. The main difference between the upper and lower plot %is not just the ability to capture in greater detail, the fluid instabilities as they happenduring the finger development and their velocity patterns. While there 
is the impact of the second injection interval as this can be seen from the slope and the rate that the velocity magnitude is changing.}
\label{fig:vel_magn}
\end{figure}
